\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Remove leftover recent accretion statement
Add uncertainties and definitions

\usepackage{setspace}
\onehalfspacing
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage[sort&compress,super]{natbib}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{aas_macros}
\usepackage{hyperref}
\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
\usepackage{mathptmx}
\usepackage{threeparttable}

@@

$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    &               \\

@@

$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 &               \\

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).

@@

% coevality based on stellar parameters
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (\figname~\ref{fig:yyisofitting}).

@@

What triggered the planet engulfment in the two comoving stars
within the last $\sim 1$~Gyr remains unclear.
One possibility is that a fly-by interaction with a field star could have
triggered eccentricity excitation of outer planets around each star, which may
have propagated inward through planet-planet scattering,
leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
If this is the case, there may be surviving, highly-eccentric giant planets.
The two stars have not been included in any publicly released data from planet
search programs, however, outer eccentric planets are potentially detectable
with future data releases of the \gaia\ mission.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.

>>>>

\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage[sort&compress,super]{natbib}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{aas_macros}
\usepackage{hyperref}
\hypersetup{backref,breaklinks,colorlinks,citecolor=blue}
\usepackage{mathptmx}
\usepackage{threeparttable}

@@

$v\sin{i}$              & \kms\          & 1.1                    & 2.5                    & 0.5           \\

@@

$A(\elem{Li})$\tnote{c} &                & $2.25$                 & $2.75$                 & 0.05          \\

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search\cite{2017AJ....153..257O} for comoving stars using the
proper motions and parallaxes from the {\it Tycho-Gaia Astrometric Solution}
catalog (hereafter \tgas), a component of the first data release of the
astrometric space mission \gaia\cite{2016A&A...595A...2G} (the astrometric
measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA\ were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(Table~\ref{tab:t1}).
The abundances are noted as \elemH{X}, defined as the log ratio of number
density of element \elem{X} to \elem{H} relative to the solar value
($\elemH{X} = \log_{10} ((n_X / n_H) / (n_X / n_H)_\odot)$).
Using the same spectra, lithium lines were modelled in Myles \etal, in prep.
For lithium, we use the absolute abundance defined as $A(\elem{Li}) = 12 +
\log_{10} (n_\elem{Li}/n_\elem{H})$.

@@

% coevality based on stellar parameters
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with effective temperature, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (\figname~\ref{fig:yyisofitting}).

@@

What triggered the planet engulfment in the two comoving stars remains unclear.
One possibility is that a fly-by interaction with a field star could have
triggered eccentricity excitation of outer planets around each star, which may
have propagated inward through planet-planet scattering,
leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
If this is the case, there may be surviving, highly-eccentric giant planets.
The two stars have not been included in any publicly released data from planet
search programs, however, outer eccentric planets are potentially detectable
with future data releases of the \gaia\ mission.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.
